Reply to reviewers concerning submission sensors-238686: "An efficient audio coding scheme for quantitative and qualitative large scale acoustic monitoring using the sensor grid approach"

### 2017-11-15 paper/articleV2.tex
acticle revision

In the case of urban acoustic monitoring, the data of interest typically rely on standardized high-quality measurements of energetic indicators such as the equivalent sound level $L_{eq}$ in dB SPL or its A-weighted counterpart $L_{Aeq}$ in dBA. However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they are not sufficient to fully describe urban sound environments \cite{rychtarikova2013}. Many other variables can be derived to better account for previously implicit properties \cite{can2016} including percentile values or time dynamics. Studies have been conducted to select relevant subsets of descriptors in sound environment characterization \cite{can2015, brocolini2013, nilsson2007}.

@@

The analysis of sources within a sound environment is generally linked with spectral content \cite{ishiyama2000} and high temporal resolutions while acoustic indicators focus on more scarce but highly accurate measurements. To the extent of our knowledge, no implementation of large-scale sensor network consider both applications using in a single measurement. We thus present in this paper an audio coding scheme specifically tailored for use in a sensor grid (case C of Figure \ref{fig:codingScheme}). The proposed method computes and encodes third-octave bands $L_{eq}$ with controllable precision, enabling low bitrate transmissions while allowing both the derivation of other acoustic indicators and the implementation of offline audio event detection schemes. We report equivalent performance of several state-of-the-art classification models from features computed using raw audio data and encoded data at production level rates. Finally, according to a perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.

@@

\section{Encoding scheme} \label{sec:coder}

\subsection{Data content}

@@

Regarding the analysis error, we consider the Matlab \textit{ita\_toolbox} implementation \cite{itatoolbox2017} as a reference, with less than $0.1~dB$ error when compared to a class 1 sound level meter on 2~s third-octave bands measurements. We study both "fast" computation with 125~ms windows and "slow" 1~s analysis to assess the impact of time integration. Third-octave bands are computed using the proposed method as well as the \textit{ita\_toolbox} in the same experimental conditions, then averaged over time and compared to the toolbox's measurements on longer 2~s extracts. The experiment is run for Gaussian white noise as well as urban environmental recordings: the former allows direct estimation bias evaluation, while the latter provides a simulation of real operating conditions. As the analysis frames are of short duration, poor frequency resolution and spectral leakage are expected when performing the STFT, particularly in the lower frequencies bands. For this reason we evaluate the impact of windowing functions on each band measurement error in order to potentially mitigate this loss of precision.

@@

Mel spectrograms are also computed with the \textit{rastamat} library \cite{ellis2005} to assess the relative performance of third-octave bands. STFT analysis frames are obtained by applying a Hann window on 23.2~ms of signal with 50\% (11.6~ms) overlap to allow for efficient phase recovery in further tests.

@@

For the perceptual test, 18 different sentences evenly distributed over the 4 frame rate parameters are selected for each subject. For each sentence the participant first listens to the extract and is then asked to transcribe the utterance and to rate the perceived intelligibility from 1 (not intelligible) to 5 (intelligible). The first metric is computed as the ratio of correctly transcribed words and will be referred as the intelligibility ratio (IR) in this paper. The second metric is directly the score attributed by the listener, referred as the intelligibility score (IS), which is assimilable to the OVRL metric proposed in \cite{itup835}. The other two metrics in this standard relative to the signal only (SIG) and background noise only (BAK), which are often used to evaluate speech enhancement schemes \citep{ntalampiras2008}, are not suitable for this test due to the background and signal being mixed with uncontrollable SNR by the coding process. As decoding the transmitted audio induces a framing effect unevenly distorting the input utterance, the computation of the IR appears adequate as an additional metric.

@@

Future work will focus on the use of such a sensor grid approach as part of the CENSE project where its effectiveness will be assessed in field conditions. The usefulness of more sophisticated encoding paradigms in order to further improve bitrate efficiency should also be studied.

>>>>

In the case of urban acoustic monitoring, the data of interest typically consists of standardized high-quality measurements of energetic indicators such as the equivalent sound level $L_{eq}$ in dB SPL or its A-weighted counterpart $L_{Aeq}$ in dBA. However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they are not sufficient to fully describe urban sound environments \cite{rychtarikova2013}. Many other variables can be derived to better account for previously implicit properties \cite{can2016} including percentile values or time dynamics. Studies have been conducted to select relevant subsets of descriptors in sound environment characterization \cite{can2015, brocolini2013, nilsson2007}.

@@

The analysis of sources within a sound environment is generally linked with spectral content \cite{ishiyama2000} and high temporal resolutions while acoustic indicators focus on more scarce but highly accurate measurements. To the best of our knowledge, no efficient coding scheme has been proposed for large-scale sensor network. We thus present in this paper an audio coding scheme specifically tailored for use in a sensor grid (case C of Figure \ref{fig:codingScheme}). The proposed method computes and encodes third-octave bands $L_{eq}$ with controllable precision, enabling low bitrate transmissions while allowing both the derivation of other acoustic indicators and the implementation of offline audio event detection schemes. We report equivalent performance of several state-of-the-art classification models from features computed using raw audio data and encoded data at production level rates. Finally, according to a perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.

@@

\section{Proposed encoding scheme} \label{sec:coder}

\subsection{Data representation}

@@

In order to assess the quality of the propoposed scheme's spectral measurement precision, we compare it to a widely used reference: the Matlab \textit{ita\_toolbox} implementation \cite{itatoolbox2017}. This toolbox's implementation shows less than $0.1~dB$ error on all bands when compared to a class 1 sound level meter on 2~s third-octave bands measurements. We study both "fast" computation with 125~ms windows and "slow" 1~s analysis to assess the impact of time integration. Third-octave bands are computed using the proposed method as well as the \textit{ita\_toolbox} in the same experimental conditions, then averaged over time and compared to the toolbox's measurements on longer 2~s extracts. The experiment is run for Gaussian white noise as well as urban environmental recordings: the former allows direct estimation bias evaluation, while the latter provides a simulation of real operating conditions. As the analysis frames are of short duration, poor frequency resolution and spectral leakage are expected when performing the STFT, particularly in the lower frequencies bands. For this reason we evaluate the impact of windowing functions on each band measurement error in order to potentially mitigate this loss of precision.

@@

Mel spectrograms are also computed with the \textit{rastamat} library \cite{ellis2005} to assess the relative performance of third-octave bands. STFT analysis frames are obtained by applying a Hann window on 23.2~ms of signal with 50\% (11.6~ms) overlap to allow for efficient phase recovery.

@@

Several subjective intelligibility metrics are standardized in the literature such as the system proposed in \cite{itup835}. However, metrics regarding the signal only (SIG) or background noise only (BAK) which are often used to evaluate speech enhancement schemes \citep{ntalampiras2008}, are not suitable for this test due to the background and signal being mixed with an uncontrollable SNR by the encoding process. Given these conditions a subjective score on the whole signal is used similarly to the OVRL score. As decoding the transmitted audio induces a framing effect unevenly distorting the input utterance, a second metric is designed to assess the comprehension of words. For the perceptual test, 18 different sentences evenly distributed over the 4 frame rate parameters are selected for each subject. For each sentence the participant first listens to the extract and is then asked to transcribe the utterance and to rate the perceived intelligibility from 1 (not intelligible) to 5 (intelligible). The first metric is directly the score attributed by the listener, referred as the intelligibility score (IS). The second metric is computed as the ratio of correctly transcribed words and will be referred as the intelligibility ratio (IR) in this paper.

@@

Future work will focus on the use of such a sensor grid approach as part of the CENSE project where its effectiveness will be assessed in field conditions. The usefulness of more sophisticated encoding paradigms in order to further improve bitrate efficiency should also be studied, as well as the effect of multiple channel coding and its interest in sensor grids applications.

### 2017-11-15 paper/sensors/coverLetter.tex
acticle revision

$\rightarrow$

@@

$\rightarrow$

@@

$\rightarrow$

@@

$\rightarrow$

@@

$\rightarrow$

@@

$\rightarrow$

@@

$\rightarrow$

@@

$\rightarrow$

@@

$\rightarrow$

@@

$\rightarrow$

@@

$\rightarrow$

@@

$\rightarrow$

@@

$\rightarrow$

@@

$\rightarrow$

@@

$\rightarrow$

>>>>

$\rightarrow$ This is now more clearly dscussed in the introduction as well as in the conclusion where a dedicated paragraph has been added.

@@

$\rightarrow$ While a single audio channel was selected for this study, a multiple channel encoding can be performed by applying the Delta compression along both the time and channels dimensions. As the transmitted data primarily consists of energetic measurements, additional channels are likely to be encoded very efficiently due to the redundance of information already contained in the first channel.

@@

$\rightarrow$ The typos have been corrected and the whole manuscript has been carefully scrutinized. The use of "we" has also been reduced to favor third-person writing. The equation numeration has been corrected throughout the document.

@@

$\rightarrow$ Following this comment as well as the comment of Reviewer III, we reworked the introduction to match this format. The considerations on acoustic monitoring and event detection in urban sound environments previously discussed in Section 2 have also been moved earlier in the introduction. A new section (Section 2.1) was added to discuss the choice of data representation.

@@

$\rightarrow$ We added a new figure (Figure 6) to clarify the applied classification process.

@@

$\rightarrow$ Our coding scheme must observe several constraints, namely low bitrate, measurement accuracy for monitoring purposes, the ability to perform event classification on the transmitted data and inintelligibility for privacy concerns. For each of these required properties we designed a validation procedure using urban environmental sound recordings. We acknowledge that the listening test is somewhat informal, as our goal is more to provide insights about why the transmitted data will not lead to intelligible speech content than to fully prove it which would be out of the scope of this paper.

@@

$\rightarrow$ The main contribution of this work, which is now more clearly shown in the introduction, is about the definition of a coding scheme that will be used (as stated in the conclusion) in a sensor network. But prior to this usage, several properties needed to be validated, motivating this work.

@@

$\rightarrow$ We added more references bewteen sections to facilitate the reader's orientation in the manuscript.

@@

$\rightarrow$ A new section (Section 2.1) has been added to motivate the use of third-octave bands for both acoustic monitoring and audio event detection.

@@

$\rightarrow$ The contribution is now more clearly stated in the introduction.

@@

$\rightarrow$ As is now explained in Section 3.2, we do not aim at achieving the best classification performance but 1) to prove that third-octave bands match the most commonly used descriptors for the classification task, and 2) to discuss the effect of encoding parameters on the recognition accuracy to select the most appropriate. To this aim we chose to replicate the baseline results for the considered dataset on these four schemes.
The study of more advanced classification schemes and of deep learning for AED will however be of particular interest in future related work.

@@

$\rightarrow$ This would be a very interesting avenue of research that could be considered for future work.

@@

$\rightarrow$ As stated in the introduction and conclusion, the proposed scheme will be applied to a sensor grid as part of the CENSE project. However, as this sensor grid is not yet implemented, the UrbanSound8k dataset provides both a decent amount of audio data with similar content (urban environmental sounds) and classification methods and results that can be used as a baseline for our work.

@@

$\rightarrow$ The contribution of this work is on the coding only. To the best of our knowledge the proposed approach is the only scheme where the data transmitted is not the detected events nor the raw audio but an intermediate spectral based format, specifically designed for acoustic monitoring and AED.

@@

$\rightarrow$ While we are aware that standardized metrics exist such as the ITU protocols, we believe that they are not adapted to the evaluation of intelligibility in this application. The encoding process distorts the signal in a very non-linear way, so that we have no control over the background and signal elements. A five-point score on the overall intelligibility is however used, and a second metric (the transcription ratio) is designed to account for the typical distortions induced by linearly scaled spectrogram and phase recoveries. Motivation and insight concerning the used metrics are now added in Section 3.3.
